Recent Advancements in Neural Computation: \\ \large Differentiable Neural Computers and End-To-End Memory Networks

### 2018-06-16 Paper/Paper.tex
fixing notation

\subsection{Architecture}
\paragraph{Overview}
An end-to-end memory network receives two inputs; a sequence of vectors $\{\pmb{x}_1,\dots,\pmb{x}_N\}$ and a query $\pmb{q}$. Both $\pmb{x}_i$ and $\pmb{q}$ are defined as symbols originating from a vocabulary $\mathcal{V}$. The network processes these inputs to return an answer $\pmb{a}$. This output is produced by first constructing continuous representations for both the input sequence and the query, and then iterating over these representations in many \textit{hops}, i.e. computational steps. The authors treat two different cases of this process; the first and simplest one employing a single layer, and the second, more general one, employing multiple layers. As this approach is favorable for understanding the architecture, we are also going to follow along the same route, modulo a few minor alterations and clarifications.

\paragraph{Single-Layer Case} First, note that a symbol $x$ from a strictly total-ordered vocabulary $\mathcal{V}$ can be uniquely represented as a vector $\pmb{x} \in \mathbb{R}^{V}$, where $V = ||\mathcal{V}||$ the size of the vocabulary. This is often referred to as \textit{one-hot encoding}. Given a character $x$ that coincides with the i-th element of $\mathcal{V}$, one-hot encoding is achieved by mapping $x$ to a vector $\pmb{x}$ whose elements are all $0$, except the $i$-th element which is $1$. This is the assumed form of input representation for the sequence $\{\pmb{x}_i\}$ and the query $\pmb{q}$.

@@

The ingenuity of this last equation is perhaps masked by its simplicity. It essentially accounts for a form of soft attention; the query dictates which parts of the output representation to focus on, depending on how it matched with the input representation. In other words, even though we always get the same output representation sequence $\{\pmb{c}_i\}$ from some input sequence $\{\pmb{x}_i\}$, the query $\pmb{q}$ plays an important role on how the network utilizes it.

>>>>

\subsection{Architecture}
\paragraph{Overview}
An end-to-end memory network receives two inputs; a sequence of vectors $]\pmb{x}_1,\dots,\pmb{x}_N]$ and a query $\pmb{q}$. Both $\pmb{x}_i$ and $\pmb{q}$ are defined as symbols originating from a vocabulary $\mathcal{V}$. The network processes these inputs to return an answer $\pmb{a}$. This output is produced by first constructing continuous representations for both the input sequence and the query, and then iterating over these representations in many \textit{hops}, i.e. computational steps. The authors treat two different cases of this process; the first and simplest one employing a single layer, and the second, more general one, employing multiple layers. As this approach is favorable for understanding the architecture, we are also going to follow along the same route, modulo a few minor alterations and clarifications.

\paragraph{Single-Layer Case} First, note that a symbol $x$ from a strictly total-ordered vocabulary $\mathcal{V}$ can be uniquely represented as a vector $\pmb{x} \in \mathbb{R}^{V}$, where $V = ||\mathcal{V}||$ the size of the vocabulary. This is often referred to as \textit{one-hot encoding}. Given a character $x$ that coincides with the i-th element of $\mathcal{V}$, one-hot encoding is achieved by mapping $x$ to a vector $\pmb{x}$ whose elements are all $0$, except the $i$-th element which is $1$. This is the assumed form of input representation for the sequence $[\pmb{x}_1,\dots]$ and the query $\pmb{q}$.

@@

The ingenuity of this last equation is perhaps masked by its simplicity. It essentially accounts for a form of soft attention; the query dictates which parts of the output representation to focus on, depending on how it matched with the input representation. In other words, even though we always get the same output representation sequence $[\pmb{c}_1,\dots]$ from some input sequence $[\pmb{x}_1,\dots]$, the query $\pmb{q}$ plays an important role on how the network utilizes it.
